---
title: "Curriculum vitae with track record"
output:
  word_document:
    reference_docx: cv-nfr_style.docx
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
# Packages and options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(flextable)
library(readxl)
library(dplyr)
library(RefManageR)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "numeric", cite.style = 'alphabetic', sorting = "none", no.print.fields = c("issn", "pages"))

# Personalization for Google Scholar
id <- 'bat21o8AAAAJ&hl' # Google Scholar ID.
sn <- scholar::get_profile(id)
p <- scholar::get_publications(id)
cit_hist <- scholar::get_citation_history(id)
```

<!-- FOR NFR FORMÅL -->
[* ROLE IN THE PROJECT]{custom-style="BigFont"}   Project manager  []    Work package leader  []    Project partner  []

# * PERSONAL INFORMATION

```{r ft.align="left"}
pinf <- tribble(
  ~Col1, ~Col2, ~Col3, ~Col4,
  "*Family name, First name:", "Sondre Aa., Nilsen ", "", "", 
  "*Date of birth:",           "18.09.1989", "*Sex:", "Male",
  "*Nationality:",             "Norwegian", "", "",
  "Researcher unique identifier(s)\n(ORCID, ResearcherID, etc.):", "0000-0002-3179-1277", "", "",
  "URL for personal website:", "...", "", "") 

pinf <- flextable(pinf)
pinf <- theme_box(pinf)

pinf %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  merge_at(i = 1, j = 2:4) %>%
  merge_at(i = 3, j = 2:4) %>% 
  merge_at(i = 4, j = 2:4) %>% 
  merge_at(i = 5, j = 2:4) %>% 
  width(j = 1, width = 2.2) %>% 
  width(j = 2, width = 3.2) %>% 
  height(i = 4, height = .5) 

```

# * EDUCATION

```{r employment, results = 'asis'}
edu <- tribble(
  ~Year, ~Institution,
  "", "Name of faculty/department, name of university/institution, country",
  "2017-2020", "Ph.D., University of Bergen, Bergen, Norway",
  "2012-2017", "Cand. Psychol, University of Bergen, Bergen, Norway")

edu <- flextable(edu)
edu <- theme_box(edu)

edu %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = 5.8) %>% 
  bg(i = 1, j = 1, "#f2f2f2")
```

# * POSITIONS

## Current Position

```{r work, results='asis'}
library(tibble)
curpos <- tribble(
  ~ Year, ~ Institution,
  "", "Job title/name of employer/country",
  "2020-", "Senior Researcher, Regional Centre for Child and Youth Mental Health and Child Welfare (RKBU-Vest),
  NORCE Norwegian Research Centre,    Bergen, Norway",
  "2020-", "Online Mentor/Supervisor, Høyskolen Kristiania, Oslo, Norway",
  "2019-", "External Examiner, University of Tromsø, Norway",
  "2018-", "External Examiner, University of Bergen, Norway",
  )

curpos <- flextable(curpos)
curpos <- theme_box(curpos)

curpos %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = 5.8) %>% 
  bg(i = 1, j = 1, "#f2f2f2")
  
```

## Previous positions held

```{r prev_work, results='asis'}
prevpos <- tribble(
  ~ Year, ~ Institution,
  "",             "Job title/name of employer/country",
  "2017-2020",    "Ph.D-Student, RKBU-Vest, Norwegian Research Centre NORCE, Bergen Norway",
  "2017-2018",    "Clinical Psychologist (20% position), Kronstad DPS, OCD-Team, Bergen, Norway",
  "2013-2017",    "Teaching Assistant, Faculty of Psychology, University of Bergen, Norway",
  "2013-2017",    "Research Assistant (20% position), Uni Research Health, Bergen, Norway"
  )

prevpos <- flextable(prevpos)
prevpos <- theme_box(prevpos)

prevpos %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = 5.8) %>% 
  bg(i = 1, j = 1, "#f2f2f2")
  
```

# FELLOWSHIPS, AWARDS AND PRIZES

```{r awards, results='asis'}
fap <- tribble(
  ~ Year, ~ Institution,
  "",        "Name of institution/country",

"2017-2020", "Extra foundation, project funding (Funding for Ph.D.) ",
"2018", "Summer scholarship for student Sunde, E.V., RKBU-Vest, Bergen, Norway",
"2014-2016", " Summer scholarships, RKBU-Vest, Bergen, Norway"
) 

fap <- flextable(fap)
fap <- theme_box(fap)

fap %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = 5.8) %>% 
  bg(i = 1, j = 1, "#f2f2f2")

```

# MOBILITY

<!-- ## Research stays abroad lasting more than three months  -->
```{r mobility, results='asis'}
#mob <- tribble(
#  ~ Year, ~ Institution, 
#  "",      "Name of faculty/department/centre, name of university/institution/country",
#   "2005", "Honours Thesis, University of New South Wales, Australia"
# ) 
#
#mob <- flextable(mob)
#mob <- theme_box(mob)
#
#mob %>% align(align="left", part="all") %>% 
#  align(align="left", part="all")  %>% 
#  align_text_col(align = "left") %>% 
#  font(fontname = "Calibri") %>% 
#  delete_part(part = "header") %>% 
#  width(j = 1, width = 1.2) %>% 
#  width(j = 2, width = 5.8) %>% 
#  bg(i = 1, j = 1, "#f2f2f2")
```

# PROJECT MANAGEMENT EXPERIENCE

<!-- ## Projects funded by Research Council of Norway, international research programmes, private or public organisations -->
```{r project, results='asis'}
#proj <- tribble(
#  ~ Year, ~ Institution, 
#  "",          "Project and role, funding from",
#  "2020-",     "Longtrends, Work package leader, Funder: Norwegian research council (NRC)",
#  "2019-",     "New patterns - safe upringing, Researcher, Funder: NRC",
#  "2014-",     "Linkage of youth@hordaland to national registries for education, Leader, Funder: NRC",
#  "2014-",     "Linkage of youth@hordaland to national patient registry, Researcher, Funder: NRC",
#  "2018-",     "The road to independence, Researcher, Funder: Wøyen foundation",
#  "2006-",     "Bergen Child Study/youth@hordaland studien, Researcher, Funder: NRC and others",
#  "2014-",     "EBU project, Researcher, Funder: NRC",
#  "2016-",     "Project Perfect, Researcher, Funder: Extra foundation",
#  "2014-2017", "Social inequalities, educational attainment and mental health (UNGSES), Leader, Funder: NRC",
#  "2016-2017", "Survey of living conditions in Askøy and Sotra, Leader, Funder: Municpalities",
#) 
#
#proj <- flextable(proj)
#proj <- theme_box(proj)
#
#proj %>% align(align="left", part="all") %>% 
#  align(align="left", part="all")  %>% 
#  align_text_col(align = "left") %>% 
#  font(fontname = "Calibri") %>% 
#  delete_part(part = "header") %>% 
#  width(j = 1, width = 1.2) %>% 
#  width(j = 2, width = 5.8) %>% 
#  bg(i = 1, j = 1, "#f2f2f2")
```

# SUPERVISION OF GRADUATE STUDENTS AND RESEARCH FELLOWS

```{r supervision, results='asis'}
####### FOR ALTERNATIVE/OLD TEMPLATE ######
 sup <- tribble(~ Year, ~ Institution,
                "", "", 
 "2018-2019",   "Masters thesis, Loro, L.P.J",
 "2017-2018",   "Seminar papers, professional studies in psychology, University of Bergen, Norway",
 )

sup <- tribble(~ Year, ~number, ~level, ~ Institution,
"", "No. of", "Master’s students/ Ph.D./Postdocs", "Name of faculty/department/centre, name of university/institution/country",
"2017-",   "1", "Master", "Faculty of Psychology, University of Bergen, Norway",
)

sup <- flextable(sup)
sup <- theme_box(sup)

sup %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = .8) %>% 
  width(j = 3, width = 1.1) %>% 
  width(j = 4, width = 3.9) %>% 
  height(i = 1, height = .7) %>% 
  bg(i = 1, j = 1, "#f2f2f2")
```

# TEACHING ACTIVITIES

```{r confpres, results='asis'}
teach <- tribble(
  ~ Year, ~ Institution,
  "",       "",
  "2019",  "Structural equation modeling with Lavaan, Katmandu,Nepal", 
  "2017",   "Mental health problems in childhood, RKBU-Vest, Bergen, Norway" ,
  "2013-2017","Seminar leader in subjects Psyk 100, Psyk 101, Psyk 102, Exfac, University of Bergen, Norway " , 
) 

teach <- flextable(teach)
teach <- theme_box(teach)

teach %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = 5.8) %>% 
  bg(i = 1, j = 1, "#f2f2f2")
```

# ORGANISATION OF MEETINGS

```{r scimeetings, results='asis'}
##meet <- tribble(
#  ~ Year, ~Institution,
#  "",     "Role and name of event/number of participants/country",
#  "2020", "Professionally responsible, Norwegian conference on Social and Community Psychology", 
#  "2017", "Professionally responsible, RKBU Conference, 400 participants, Norway"
#) 
#
#meet <- flextable(meet)
#meet <- theme_box(meet)
#
#meet %>% align(align="left", part="all") %>% 
#  align(align="left", part="all")  %>% 
#  align_text_col(align = "left") %>% 
#  font(fontname = "Calibri") %>% 
#  delete_part(part = "header") %>% 
#  width(j = 1, width = 1.2) %>% 
#  width(j = 2, width = 5.8) %>% 
#  bg(i = 1, j = 1, "#f2f2f2")
```


# INSTITUTIONAL RESPONSIBILITIES

<!-- ## Member of a committee/graduate student advisor etc.  -->

```{r institu, results='asis'}
#instres <- tribble(
#  ~ Year, ~Institution,
#"2019-", "Revision of psychology education (Rethos), Faculty of Psychology" ,
#"2017-", "PhD theses advisor",
#"2015-", "Masters theses advisor" 
#) 
#
#instres <- flextable(instres)
#instres <- theme_box(instres)
#
#instres %>% align(align="left", part="all") %>% 
#  align(align="left", part="all")  %>% 
#  align_text_col(align = "left") %>% 
#  font(fontname = "Calibri") %>% 
#  delete_part(part = "header") %>% 
#  width(j = 1, width = 1.2) %>% 
#  width(j = 2, width = 5.8) %>% 
#  bg(i = 1, j = 1, "#f2f2f2")

```

# COMISSIONS OF TRUST

<!-- ## Scientific advisory board/review board/review panel member/editorial board/scientific advisory board/reviewer/scientific evaluation/etc.  -->

```{r trust, results='asis'}
trust <- tribble(
  ~ Year, ~ Institution,
  "",           "Name of university/institution/country – and role",
  "2018 -",  "Reviewer Journal of Affective Disorders" ,
)

trust <- flextable(trust)
trust <- theme_box(trust)

trust %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 1.2) %>% 
  width(j = 2, width = 5.8) %>% 
  bg(i = 1, j = 1, "#f2f2f2")
```

<!-- # Membership of academies/scientific societies -->
<!-- \vskip -.15 in -->

# Major collaborations

```{r}
collab <- tribble(
  ~ Where, ~ Institution,
  "Name of university/ institution/ faculty/ department/ centre, company/ governmental or non-governmental organisation", "Topic",
  "NORCE Norwegian research centre, Bergen Child study",
  "Department of Psychosocial Science (UiB), Research group for public mental health"
  )



collab <- flextable(collab)
collab <- theme_box(collab)

collab %>% align(align="left", part="all") %>% 
  align(align="left", part="all")  %>% 
  align_text_col(align = "left") %>% 
  font(fontname = "Calibri") %>% 
  delete_part(part = "header") %>% 
  width(j = 1, width = 4) %>% 
  width(j = 2, width = 3) %>% 
  height(i = 1, height = .7)
```


### Track record

<!-- 1.	The total number of publications during the career. -->
<!-- 2.	A list of up to ten publications in major national or international peer-reviewed multidisciplinary scientific journals and/or in the leading national or international peer-reviewed journals, peer-reviewed conferences proceedings and/or monographs of their respective research fields. Indicate, if possible, the number of citations (excluding self- citations). -->
<!-- 3.	Research monographs and any translations thereof (if applicable).  -->
<!-- 4.	Granted patent(s) (if applicable). -->
<!-- 5.	Examples of leadership/participation in industrial or public innovation or design and/or highlights from research or innovation with societal impact (if applicable). -->
<!-- 6.	Leadership of field work or research expeditions (if applicable).	 -->
<!-- 7.	Invited presentations to peer-reviewed national or international conferences and/or international advanced schools (if applicable). -->
<!-- 8.	Experiences from major research communication, dissemination or outreach activities and/or invited presentations in public conferences (if applicable). -->

```{r, echo=FALSE, message=F, warning=F}
# For automatically updating the track record
## Authorships
first_lastauthor <- bibliography_entries("pubs.bib") %>% # Change to file containing your own references!
  filter(bibtype == "Article") %>% 
  select(author) %>% 
  as.data.frame(.)

auth_split <- separate(first_lastauthor, col = "author", into=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"), sep = "and", remove = FALSE, fill = "right")
auth_split2 <- auth_split[2:11]

lastValue <- function(x)   tail(x[!is.na(x)], 1)
firstValue <- function(x)   head(x[!is.na(x)], 1)

firstauthor <- as.data.frame(apply(auth_split2, 1, firstValue))
colnames(firstauthor) <- "first"
lastauthor <- as.data.frame(apply(auth_split, 1, lastValue))
colnames(lastauthor) <- "last"

n_firstauthor <- firstauthor %>% dplyr::filter(stringr::str_detect(first, "Nilsen")) %>% count() # Replace Bøe with own surname.
n_lastauthor <- lastauthor %>% dplyr::filter(stringr::str_detect(last, "Nilsen")) %>% count()    # Replace Bøe with own surname.

## Dissemination
formidling <- read_excel("Formidling.xlsx", sheet = "Ark2") # Change to file with own dissemination activities.
saveRDS(formidling, "formidling.rds")
n_delt <- formidling %>% select("Antall deltagere") %>% colSums(.)
startår <- formidling %>% select(År) %>% min()
slutttår <- formidling %>% select(År) %>% max()
```




I have authored or co-authored a total of `r length(unique(p$pubid))` publications. I am the first author of `r n_firstauthor` peer reviewed journal articles and the senior author on `r n_lastauthor`. My articles have been cited `r sn$total_cites` times, my _h_-index is `r sn$h_index` and my _i10_-index is `r sn$i10_index` [according to Google Scholar](https://scholar.google.com/citations?user=bat21o8AAAAJ&hl=en). _(Updated `r format(Sys.Date(), "%d.%m.%Y")`)_. Further details available upon request.


```{r fig1, fig.retina=2}


ggplot2::ggplot(cit_hist, aes(year, cites)) + 
  geom_line() + 
  geom_point() +
  ggthemes::theme_fivethirtyeight(base_size = 10) +
  theme(panel.background = element_rect(fill = "white"), plot.background = element_rect(fill = "white")) +
  theme(axis.title = element_text()) +
  scale_x_continuous(breaks = 0:2100) +
  labs(title = "Fig. 1 Citations pr year",
       subtitle = "Source: Google Scholar") +
      ylab('Citations') + xlab("Year")
  
```



<br><br><br><br><br>

Selected publications:  

<br><br><br><br><br>

```{r trackrefs, results='asis'}
bib<- ReadBib("pubs.bib",check= FALSE)
bib %>% as_tibble() %>% filter(!is.na(ids)) %>% 
  mutate(ids = as.numeric(ids)) %>% 
           arrange(ids) %>% 
  as.BibEntry() 
```

\newpage

# LIST OF PUBLICATIONS

## PhD Thesis

```{r, results='asis'}
bib %>% as_tibble() %>% filter(bibtype == "PhdThesis") %>% 
  arrange(desc(year)) %>%  #Bytte "date" med "year"
  as.BibEntry(.)
```

## Refereed research papers 

```{r articles, results='asis'}
bib %>% as_tibble() %>%
  filter(bibtype == "Article") %>%
  # filter(date>2013) %>%
  arrange(desc(year)) %>% #bytte date med year
  as.BibEntry(.)
```

## Books and book chapters
```{r books, results='asis'}
#bib %>% as_tibble() %>%
#  filter(bibtype == "InCollection")  %>% 
#  as.BibEntry(.)
```

## Conference proceedings
```{r conference, results='asis'}
#bib %>% as_tibble() %>%
#  filter(bibtype == "InProceedings") %>%
#  arrange(desc(date))  %>% 
#  as.BibEntry(.)

```

## Reports

```{r, results='asis'}
#bib %>% as_tibble() %>%
#  filter(bibtype == "Report") %>% 
#  as.BibEntry(.)
```



